---
title: "Untitled"
output: html_document
date: "2024-05-18"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
knitr::opts_chunk$set(echo = TRUE)

source(here::here("00_helpers.R"))
source(here::here("01b_load_data.R"))

mv_long$tones = gsub("deaccented", "DA", mv_long$tones)
dz_long$tones = gsub("deaccented", "DA", dz_long$tones)
long_all$tones = gsub("deaccented", "DA", long_all$tones)
```

Hi Brandon, 

Thanks for the quick feedback on this! I'm responding here to your email in my time on `May 17, 2024, 8:47 PM`. I am doing this here and will update the graphs in the other link (https://kparrish92.github.io/goodale_consult/plots_5_17.html) once we sort out the issues. I've quoted you below in italics, while my responses are in block quotes. I am including the code used to filter the data, so that you can see and we can figure out where a problem might be. 


*Graph 2: Concerns me. IT should be Montevideo non-focalized prenuclear pitch accents (combined count of prenuclear BFD and prenuclear non-focalized NFD PWs) (not by gender or age). As such it should not have any nuclear pitch accents which I can see it does because nuclear pitch accents have % boundary tones. I do not mean chop off the boundary tones, I mean don't include pitch accents that I originally coded with a - or % boundary tone. This same data should be used for Graphs 4 and 6. This same issue as Graph 2 appears in Graph 15*

```{r, echo = TRUE}
check_graph2_data = mv_long %>% 
  filter(is.na(focused) & position != "N") %>%  
  filter(str_detect(tones, "%"))

print(check_graph2_data)
```

> It looks like the items containing % come from NFD4. The code takes a data set called "mv_long", which is the Montevideo data in a long format. It then filters the data for only non-focused and prenuclear tokens, and then any tone containing the symbol "%". It shows that 29 out of 960 rows contiain %, which all happen to be NFD4. Should NFD4 be marked as focused? 